Data- and Ontology Paper: Quality Ontology for Handicap Parking Spots around Venues in Amsterdam

### 2016-04-23 milestone2/paper/paper.tex
started discussion section

% a short form should be given in case it is too long for the running head
\titlerunning{Data- and Ontology Paper}

@@

\section{Discussion}
\textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}

>>>>

% a short form should be given in case it is too long for the running head
\titlerunning{Quality Ontology for Handicap Parking Spots around Venues in Amsterdam}

@@

\section{Discussion}
% \textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
In this paper we provided a detailed description of the improved ontology that
we have published about three datasets related to the city of Amsterdam.
Moreover we show the methodology that we adopted and how this led our ontology
to be classified as fully conform with the 5-star model for Linked Data.
Being conform to this model for Open Data means that publishers will ultimately
have a dataset that is easily \textit{surfable} and \textit{connected} with
other Web resources, generating more incoming traffic towards the dataset and
increasing the value of the contained data. The 5-star model is a way to
introduce sources of \textit{trust} in both the data and publishers' spaces.
In particular we have found very useful and powerful the set of propositions offered
by the VoID framework and how easy it is to define \textit{discoverable}
ontologies using Web standards.
